### 2021-06-15 README.Rmd
added some files with my paper and talk, prepped for publishing to CRAN

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
[![Codecov test coverage](https://codecov.io/gh/srmatth/mshap/branch/main/graph/badge.svg)](https://codecov.io/gh/srmatth/mshap?branch=main)
<!-- badges: end -->
